Adaptive Hierarchical Sliding Mode Control with Input Saturation for Attitude Regulation of Multi-satellite Tethered System

### 2016-07-10 manuscript.tex
20160710

The tethered satellite system (TSS) consists of the orbiting satellites connected by long thin space tethers. Since the conception of the TSS was addressed in 1960s, many space institutes have implemented such a significant number of orbital and suborbital experiments as TSS-1R, SEDS, MAST and YES2~\cite{williams2012review}, to verify the feasibility of the studies developed for the TSS from 1970s to 1980s. Among other things, the TSS has been ideally qualified for various missions in the space environment, like the electrodynamic propulsion application~\cite{lanoix2005effect}, deorbiting defunct satellites~\cite{khan2014analysis}, the space tug~\cite{wen2016constrained} and the space elevator~\cite{kojima2015mission}.\par
In recent years, many investigations have been carried out about control law designs and formation flights of the TSS, providing some effective solutions to the attitude stabilization and flight formations~\cite{misra2002equilibrium,yan2012feedback,xu2012nonlinear,zhu2015dynamic,hallaj2015tethered,alary2015dynamics,wang2015coordinated,ting2016reconfiguration,cicci2016preliminary}. Typically, for the attitude stability, the steerable thruster-based control is utilized extensively due to its convenient application~\cite{aslanov2013dynamics,jasper2014input,jasper2014tethered,aslanov2014dynamics}. However, one should take into account the fact that the availability and consumption of the fuel restrict the work of actuators directly, leading the control to be short-term~\cite{chung2008propellant1}, and moreover, in traditional thruster-based control schemes, there exists a fatal impact of the jet propulsive working medium on the sensors and the neighbour satellites~\cite{hallaj2015tethered}.\par
To alleviate these concerns of the thruster-based control, some alternative non-pure thruster-based schemes for formation flights of the TSS have been proposed. Miller addressed the concept of the electromagnetic formation flying (EMFF), in which the high temperature superconducting technology was employed to regulate the attitude indirectly~\cite{miller2010control}. Some researches followed to achieve EMFF by using different control schemes~\cite{zhang2014adaptive,huang2015lmi}. \begin{color}{red}Zhong et al. reported the application of electrodynamic tether for nanosatellite fast deorbit in low earth orbit~\cite{zhong2013dynamics}, and also presented a piecewise two-phased optimal control scheme to achieve open-loop control trajectory optimization~\cite{zhong2014optimal}.\end{color} Yang investigated the three-inline satellite array, in which the participating satellites were equipped with the reaction wheels and the thrusters, and hence the linear force and the flywheel torque cooperated to manipulate the spacecraft~\cite{yang2015decentralized}. Natarajan and Schaub combined the Coulomb forces with conventional thrust forces to obtain a control scheme, in which the Coulomb forces predominated, and investigated the stability of the two-craft formation about different equilibrium configurations~\cite{natarajan2009hybrid}. In the view of canceling the drawback of the thrusters in the attitude regulation control, as a inter-force actuator, the utilization of flywheels has been focused on~\cite{pizarro2008dynamics}. Comparing to the thruster-based scheme, the solar sails providing the power for the flywheels can achieve a long-term control, and simultaneously the contamination to the sensitive sensors does not occur. However, in the absence of the thrusters forces, the pure flywheel torque control causes the attitude dynamics underactuated adversely, i.e., Chung et al. introduced the concept of the underactuated multi-satellite inline system, and proposed the underactuated control scheme for the compound pendulum dynamics of the TSS~\cite{chung2008propellant1}.\par
Besides actuator selection, the effective control scheme and the formation type are both important components of the TSS. In recent years, many researchers strived to investigate the motion dynamics of the multi-satellite inline formation, and there have existed a variety of sophisticated linear control schemes. Chung et al. exploited geometric symmetries to derive the reduction dynamics, and addressed the decentralized linear control method for the flight tailored toward the SPECS mission~\cite{chung2007nonlinear}. They also developed a gain-scheduling control law to adjust the attitude of the multiple-satellite system without any thruster forces~\cite{chung2008propellant1}. Yang et al. proposed the decentralized fault tolerance control scheme for the attitude of the satellites in the three-inline array around the equilibrium point~\cite{yang2015decentralized}. In the aspect of nonlinear control, Chung et al. presented a backstepping control design for the multi-satellite system after reducing the model into the strict-feedback cascade normal form~\cite{chung2008propellant2}. Zhao et al. applied gauss pseudospectral method to multi-objective trajectory optimization for two spacecrafts~\cite{zhao2014gauss}. Characteristically, among the strategies mentioned above, all the inputs are referred to as unsaturated behaviors, however, in the realistic application the input saturation frequently does occur. Even further, this unexpected situation often leads controllers to no longer ensure the performance of regulation objective practically~\cite{zavala2007natural}. The existence of the saturation, which usually stems from the physical mechanics and the energy dissipation, can result in the fatal differential between the desired control signal and the actual output effort of the actuator, and essentially it becomes a potential source of the corruption~\cite{Hu2009Robust}. In order to resist the effect of the saturation, Bo{\v{s}}kovi{\'{c}} et al. proposed global stable control algoritheorems with variable structure philosophy presence of control input saturation~\cite{bovskovic2001robust}; Tsiotras and Luo decoupled the general motion dynamics into two rotations, and designed a feedback control scheme to regulate the system to track a specified state in the inertial space~\cite{tsiotras2000control}; Grimm et al.~\cite{grimm2003antiwindup}, Xu and Lam~\cite{xu2001robust} paid more attention to the linear systems with the bounded input. Admittedly, introducing the saturated inputs into the control systems is complicate but meaningful for both the theoretical studies and the engineering applications.\par
In this paper, a novel adaptive sliding mode control scheme is proposed for the three-satellite inline array and the two-satellite system. This work takes into consideration the characteristics of the coupling input saturation, whereas the linear force is absent in the attitude regulation of the satellite. The remainder of the paper is organized as follows. In Section~\ref{sec:mm}, the mathematical model for the flight of three-satellite inline array is presented, and a novel MHSM scheme for the stability of the attitude dynamics is proposed, with emphasis on the solution of the input saturation in Section~\ref{sec:SMC}. In Section~\ref{sec:SMC2}, the attitude dynamics of two-satellite system is investigated, and applying MHSM scheme to stabilize the attitude dynamics motion is exhibited. Finally the numerical simulation is illustrated to validate the above mentioned control design in Section~\ref{sec:sm}.

@@

\begin{color}{red} The structure of the three-satellite inline array stems from NASA's Submillimeter Probe of the Evolution of Cosmic Structure (SPECS) mission, which is famous as a tethered spacecraft interferometer, and the array keeps rotating while detecting submillimeter-wave-length light from the early universe. The structure of the three-satellite array can be seen in Figure~\ref{Figure:3satellite}. Compared with traditional two-body tethered satellite system, the two end bodies in the array can carry same instruments to observe the information to ensure accuracy of data. Also, due to the existence of the centripetal force, it is more convenient to deploy the tether while rotating the array in the deep space. In addition, some long-term spatial gravitational experiments can be developed based on this structure.\end{color}\par

@@

where $J_1$ denotes the moment of inertia of the satellite array for the vertical axis; $J_1=3I_1+2ml^2$ in which $I_1$ refers to the moment of inertia of an individual participant in the three-body inline frame; $l$ identifies the tether length connecting to the central satellite; $J_2$ has the similar expression $J_2=3I_2+2ml^2$ for the second axis. In Figure~\ref{Figure:3satellite}, the first axis is perpendicular to the rotation plane which is determined by the other two axes. Attach the third axis to the tether, and the rotation about the second axis generates the out-of-plane motion. Without loss of generality, it is quite reasonable to assume that the individual satellite is axis-symmetric thoroughly. The participating satellites arranging in a line neatly derives to $I_1=I_2$, and in addition the array is axis-symmetric about the third axis as well~\cite{chung2008propellant1}. Hence, Eq.~(\ref{eq:3body}) reduces to

@@

which brings out that the three-satellite inline tethered system torsional rotation dynamics is irrelevant to the other two axes~\cite{chung2008propellant1}. Since the dynamic state $\omega_3$ is independent from the two axes, a simple linear feedback control can regulate the flywheel torque to control the dynamics of the third axis, such that both $\omega_3=0$ and $\dot\omega_3 = 0$. Hence Eq.~(\ref{eq:3model}) reduces to

@@

\end{align} \begin{color}{red}From equations above, $\omega_2$ is independent from $\omega_1$. Similar to the dynamic state $\omega_3$, dynamic state $\omega_2$ can be controlled separately without affecting the in-plane dynamics~\cite{chung2007nonlinear,chung2007nonlinear1,chung2007nonlinear3}. For each satellite, three flywheels are mounted orthogonally to regulate the attitude. The flywheel which is mounted perpendicularly to the tether, governs the dynamic state $\omega_3$, and different from the other axes, the varying $\omega_3$ will not lead to the situation described in Figure~\ref{Figure:model3body}, hence a simple linear feedback control can achieve its attitude regulation. When we attention on the in-plane dynamics, the other two flywheel torques and thruster firing handle the out-plane dynamics, which can guarantee that the in-plane motion occurs without other disturbance from the other axes.\end{color} On the premise of the assumption that the out-of-plane plant is stable independently, the in-plane attitude dynamics, accordingly, can be described as a model consisting of three flywheels assembly and two tethers, as seen in Figure~\ref{Figure:model3body}. \begin{color}{red}The mathematical model expressed by using Euler-Lagrange equations is established, and the origin of the array is the satellite's geometrical center as well the mass center.\end{color} In the 2D plane, the three-body satellite array arranges along the $y$ direction, and the positive directions of $\theta_i$ and $\phi_i$ are anticlockwise. $F_i$ denotes the $i$th thruster's linear force, and $u_i$ is defined to be the $i$th flywheel torque acting on the center of mass. $\Psi$ identifies the rotation angle, then the dynamic equation follows~\cite{chung2007nonlinear1}

@@

Hence $\vert M_1\vert = I_gml^2+m^2r^2l^2(1-\cos^2{\phi})>0$, and $M_1$ is invertible. In the view of Lagrangian mechanics, one can get the similar result, since $M_{1}$ is a positive definite matrix~\cite{ortega2013passivity}.\end{color}

@@

Figure~\ref{Figure:modelsinglebody} shows an individual participating satellite which rotates about the center of the array frame. Body coordinate system x-y requires that y axis points to the direction of the array increasing rotation angle, and meanwhile x axis is along the tether. It is assumed that the tether is massless and inextensible so that the vibration dynamics can be regardless. The Kevlar physical property makes the tether strong and thin enough, i.e., SPECS owns the tether consisting of four tethers lines, and the total mass is approximate to 30 \textit{kg} for 1-km-long ribbon tether. The three-satellite inline tethered frame is assumed to revolve about at a specific angular rate so that the tether will keep taut eternally. Since the tether speed can be easily controlled by programmed tether motor and doesn't disturb any other system states, it¡®s assumed that the tether length speed $\dot l$ is naught. Finally, assume the three-satellite inline tethered frame is manoeuvred to orbit in the second Lagrangian point of the earth-sun system referring to the SPECS project~\cite{chung2007nonlinear}, and hence the gravity term is approximate to zero thereby.\par

@@

To our knowledge, flywheels are applied as the proper actuators frequently in the attitude regulation of the satellite, for instance, the system of the SPECS project in an orbit around the L2 lagrange point is manoeuvred by using the flywheel control strategy in most of the time~\cite{chung2008propellant1}. In the view of the mechanical structure, there are two categories of flywheels, namely, the bias moment and the zero moment. Functionally, the rotation rate of the bias moment wheels is nonnegative; the zeros moment ones can change the rotation direction. The zero moment wheels are typically known as reaction wheels, which may always maintain the whole satellite's moment zero, and are used more widely than the bias ones in the stability control of the satellite attitude. Considering the energy consumption of the system in practice, wheels are driven by the electricity which may be provided by energy harvesting system, and in contrast with the thruster, the utilization of flywheels avoids consuming the limited quantities of fuel during the attitude regulation. In the aspect of regulating accuracy, the TSS need reaction wheels to generate the continuous high precise torque for the regulation in orbit, whereas thrusters consume expensive fuel to supply the linear torque output in pulse method. In addition, the reaction wheel is convenient to equip, and there always exists a incline reaction wheel equipped as the redundancy actuator. Typically, the thruster force is crucial to deploy the satellite into specified orbit in limited time, and the reaction wheel torque regulates the attitude for a long time in orbit around the earth. For the attitude regulation, with neglecting the thruster force input, using the reaction wheel control strategy changes the three-satellite inline frame into an underactuated system. More notably, the effect of the input for the control system is saturated, since the torque of an reaction wheel is not infinite. Normally, for a reaction wheel, the positive and negative torques are identical, which can be expressed by the saturation function.

@@

where $T_p$ and $T_n$ denote the maximal positive and negative torque, respectively. According to aforementioned analysis, the equations for the dynamics of the individual satellite shown in Figure~\ref{Figure:modelsinglebody} holds

@@

Synchronization and Partial Contraction~\cite{wang2005partial}. Consider two nominal coupled system which have the relation

@@

where the function $f(x,t)$ has contracting property in an input-independent matric, then the state $x_1$ and $x_2$ will approach each other in spite of the different initial requirement.\label{theorem:syn}

@@

According to Lemma~\ref{theorem:syn}, Eq.~(\ref{eq:3bodyreduce}) indicates that the formulation of two sub-systems meets the contracting requirement, hence $(\theta_1,\phi_1)^T$ and $(\theta_1,\phi_2)^T$ will coverage to each other thereby if an individual control law is designed to guarantee the stability of the each one~\cite{huang2015nonlinear}.\par
This work ignores the linear force, and hence the system becomes underactuated and input saturated.

@@

In addition, $d_1(X,t)$ and $d_2(X,t)$ denote the external perturbations such as the gravity gradient torque, the solar pressure torque, the aerodynamic torque or the magnetic torque, and among the previous perturbations, the aerodynamic torque plays a major role, which will affect the stability of the attitude.\par
In this work, the attitude regulation of the individual satellite expressed in Eq.~(\ref{eq:model}), which can be described as an issue about the stabilization of an underactuated and coupling input system, is achieved by utilizing the variable structure theory, with emphasis on the solution of the actuators saturation. Once the states of Eq.~(\ref{eq:model}) is stable, according to Lemma~\ref{theorem:syn}, the entire three-satellite array can be adjusted to be a fixed-point rotation system.

@@

The issue about attitude regulation of the three-satellite inline tethered system is converted into designing the independent control system for the individual satellite described as Eq.~(\ref{eq:model}), and meanwhile, the system is strict saturated, coupled and nonlinear. There exists a stable \begin{color}{red}hierarchical sliding mode (HSM)\end{color} approach investigated for a class of second order underactuated systems, like Acrobot, overhead crane and pendubot etc~\cite{wang2004design}, and the state space equations of the these models are similar to the form of Eq.~(\ref{eq:model}). Considering the effect of the input saturation, synthesizing the HSM and adaptive sliding mode control schemes derives a modified method, which can overcome both the input saturation and coupling characteristics.\par

@@

s_2 = c_2x_3+x_4

@@

where $c_1$ and $c_2$ are suitable parameters and always positive. Construct the input to supply the asymptotically convergence of the second-level sliding surface:

@@

S=\alpha s_1+\beta s_2\label{eq:S}.

@@

The proceeding of HSM design is omitted. There is an important lemma mentioned for the modified approach design.

@@

Considering a sort of underactuated systems which own a stabel equilibrium point, propose the sliding surfaces as Eq.~(\ref{eq:model}), Eq.~(\ref{eq:s1s2}), Eq.~(\ref{eq:S}), and there is a approach to guaranteeing the asymptotically convergence of the second-level sliding mode. If $s_1\in L_\infty$, $\dot s_1\in L_\infty$, then the first-level sliding mode also asymptotically converges.\label{lm:1}

@@

Consider the nominal nonlinear system Eq.~(\ref{eq:model}), and rewrite $\bar{sat}(u)$ as $\bar{sat}(u) = R(u)u$. Note that $0 \le R(u) \le 1$

@@

where $u_{max}(u_{min})$ is the maximum torque that the reaction wheel can generate in positive (negative) direction, and there is a restriction $u_{min}<0<u_{max}$, $u_{min}=-u_{max}$ for guaranteeing the predefined condition $0<R(u)\le 1$.\par

@@

$d_1(X,t)$ and $d_2(X,t)$ are the uncertain parts of system~(\ref{eq:model}), and satisfies the following relation $max(\vert d_1(X,t)\vert,\vert d_2(X,t)\vert) \le \zeta <\infty$, $\zeta$ is constant positive.\label{as:2}

@@

Modified hierarchical sliding mode control (MHSM) constructs the first- and second-level surfaces in the same way, and thanks to the Lemma~\ref{lm:1} and Assumption~\ref{as:2}, we propose the adaptive control input conveniently as follows:

@@

For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $0<\alpha\le\beta$.

@@

    This can guarantee the non-singularity of Eq.~(\ref{eq:u}), because $x_3$ should be varying in a small region with $\vert x_3\vert<\pi/2$.

@@

The three-satellite inline array can be simplified as three individual satellite systems by above-mentioned model reduction technology, and in this section, a two-satellite array system shown in Figure~\ref{Figure:model2body} is investigated, in which two satellites are the participants connected with a stiff space tether. The dynamic equations of the two-satellite array system can be described as follows:

@@

where $X = (x_1,x_2,x_3,x_4,x_5,x_6)^T$. In addition, $\bar{sat}()$, $f_i(X,t)$ and $d_i(X,t)$ have the similar mathematical feature which is illustrated in the individual system of three-satellite inline array in Eq.~(\ref{eq:model}), and $f_i(X,t)$ and $b_i(X,t)$ can be derived:

@@

where $\vert\phi_1\vert<\pi/2$, $\vert\phi_2\vert<\pi/2$. Hence $M_{3}$ is invertible.\end{color}\par
For proceeding to apply the MHSM control to the attitude regulation of the two-satellite inline system shown in Eq.~(\ref{eq:2model}), the first-level iedal sliding surfaces are selected firstly as follows:

@@

    where $\vert\phi_1\vert<\pi/2$ and $\vert\phi_2\vert<\pi/2$.

>>>>

\begin{color}{red}The tethered satellite system (TSS) consists of in-orbit satellites, which are connected by long thin space tethers. Since the conception of the TSS was addressed in 1960s, many space institutes have implemented a significant number of orbital and suborbital experiments, such as TSS-1R, SEDS, MAST and YES2~\cite{williams2012review}, to verify the feasibility of the existing studies from 1970s to 1980s. \end{color}Among other things, the TSS has been ideally qualified for various missions in the space environment, like the electrodynamic propulsion application~\cite{lanoix2005effect}, deorbiting defunct satellites~\cite{khan2014analysis}, the space tug~\cite{wen2016constrained} and the space elevator~\cite{kojima2015mission}.\par
In recent years, many investigations have been carried out about the dynamics of the TSS, providing some effective solutions to the attitude stabilization and flight formations~\cite{misra2002equilibrium,yan2012feedback,xu2012nonlinear,zhu2015dynamic,hallaj2015tethered,alary2015dynamics,wang2015coordinated,ting2016reconfiguration,cicci2016preliminary}. \begin{color}{red}Typically, for the attitude stability, the steerable thruster-based control is utilized extensively due to its convenience of equipping ~\cite{aslanov2013dynamics,jasper2014input,jasper2014tethered,aslanov2014dynamics}. However, this strategy is in a dilemma about that the work of actuators is dependent on the availability and consumption of the fuel directly~\cite{chung2008propellant1}, and moreover, in thruster-based control schemes,  the propulsive working medium ejected by thrusters has an impact on the measurement of sensors in the vicinity~\cite{hallaj2015tethered}.\end{color}\par
To alleviate these concerns mentioned above, some alternative non-pure thruster-based schemes for formation flights of the TSS have been proposed. Miller addressed the concept of the electromagnetic formation flying (EMFF), in which the high temperature superconducting technology was employed to regulate the attitude indirectly~\cite{miller2010control}. Some researches followed to achieve EMFF by using different control schemes~\cite{zhang2014adaptive,huang2015lmi}. \begin{color}{red}Zhong et al. reported the application of electrodynamic tether for nanosatellite fast deorbit in low earth orbit~\cite{zhong2013dynamics}, and also presented a piecewise two-phased optimal control scheme to achieve open-loop control trajectory optimization~\cite{zhong2014optimal}.\end{color} Yang investigated the three-inline satellite array, in which the participating satellites were equipped with the reaction wheels and the thrusters, and hence the linear force and the flywheel torque cooperated to manipulate the spacecraft~\cite{yang2015decentralized}. Natarajan and Schaub combined the Coulomb forces with conventional thrust forces to obtain a control scheme, in which the Coulomb forces predominated, and investigated the stability of the two-craft formation about different equilibrium configurations~\cite{natarajan2009hybrid}. In the view of canceling the drawback of the thrusters in the attitude regulation control, as a inter-force actuator, the utilization of flywheels has been focused on~\cite{pizarro2008dynamics}. \begin{color}{red}Compared to the thruster-based scheme, the solar sails provide the power for the flywheels to achieve a long-term control, and simultaneously the contamination to the sensitive sensors does not occur. However, due to the absence of the thrusters forces, the pure flywheel torque control causes the attitude dynamics underactuated adversely~\cite{chung2008propellant1}.\end{color}\par
Besides actuator selection, the effective control scheme is also an important component of the TSS. In recent years, many researchers strived to investigate the motion dynamics of the multi-satellite inline formation, and there have existed a variety of sophisticated linear control schemes. Chung et al. exploited geometric symmetries to derive the reduction dynamics, and addressed the decentralized linear control method for the flight tailored toward the SPECS mission~\cite{chung2007nonlinear}. They also developed a gain-scheduling control law to adjust the attitude of the multiple-satellite system without any thruster forces~\cite{chung2008propellant1}. Yang et al. proposed the decentralized fault tolerance control scheme for the attitude of the satellites in the three-inline array around the equilibrium point~\cite{yang2015decentralized}. In the aspect of nonlinear control, Chung et al. presented a backstepping control design for the multi-satellite system after reducing the model into the strict-feedback cascade normal form~\cite{chung2008propellant2}. Zhao et al. applied gauss pseudospectral method to multi-objective trajectory optimization for two spacecrafts~\cite{zhao2014gauss}. Characteristically, among the strategies mentioned above, all the inputs are referred to as unsaturated behaviors, however, in the realistic application the input saturation frequently does occur. \begin{color}{red}Even further, this unexpected situation often deteriorates the performance of regulation objective practically~\cite{zavala2007natural}. The saturation usually stems from the physical mechanics and the energy dissipation, and leads to the error between the actual output and the command signal. Hence, this case can be regarded as a potential source of the corruption~\cite{Hu2009Robust}, and should be taken in account when the controller is designed.\end{color} \begin{color}{red}In order to resist the effect of the saturation, Bo{\v{s}}kovi{\'{c}} et al. proposed global stable control algorithm with variable structure philosophy to overcome input saturation~\cite{bovskovic2001robust};\end{color} Tsiotras and Luo decoupled the general motion dynamics into two rotations, and designed a feedback control scheme to regulate the system to track a specified state in the inertial space~\cite{tsiotras2000control}; Grimm et al.~\cite{grimm2003antiwindup}, Xu and Lam~\cite{xu2001robust} paid more attention to the linear systems with the bounded input. Admittedly, introducing the saturated inputs into the control systems is complicate but meaningful for both the theoretical studies and the engineering applications.\par
In this paper, a novel adaptive sliding mode control scheme is proposed for the three-satellite inline array and the two-satellite system. This work takes into consideration the characteristics of the coupling input saturation, whereas the linear force is absent in the attitude regulation of the satellite. The remainder of the paper is organized as follows. In Section~\ref{sec:mm}, the mathematical model for the flight of three-satellite inline array is presented, and a novel MHSM scheme for the stability of the attitude dynamics is proposed, with emphasis on the solution of the input saturation in Section~\ref{sec:SMC}. In Section~\ref{sec:SMC2}, the attitude dynamics of two-satellite system is investigated, \begin{color}{red}and the stability analysis of the MHSM scheme for the dynamics is exhibited.\end{color} Finally in Section~\ref{sec:sm}, the numerical simulation is illustrated to validate the proposed control design.

@@

\begin{color}{red} The structure of the three-satellite inline array stems from NASA's Submillimeter Probe of the Evolution of Cosmic Structure (SPECS) mission, which is famous as a tethered spacecraft interferometer, and the array keeps rotating while detecting submillimeter-wave-length light from the early universe~\cite{lorenzini2006far}. The structure of the three-satellite array can be seen in Figure~\ref{Figure:3satellite}. Compared with traditional two-body tethered satellite system, the two end bodies in the array can carry same instruments to observe the information to ensure accuracy of data. Also, due to the existence of the centripetal force, it is more convenient to deploy the tether while rotating the array in the deep space. In addition, some long-term spatial gravitational experiments can be developed based on this structure.\end{color}\par

@@

where $J_1$ denotes the moment of inertia of the satellite array for the vertical axis; $J_1=3I_1+2ml^2$ in which $I_1$ refers to the moment of inertia of an individual participant in the three-body inline frame; $l$ identifies the tether length; $J_2$ has the similar expression $J_2=3I_2+2ml^2$ for the second axis. In Figure~\ref{Figure:3satellite}, the first axis is perpendicular to the rotation plane which is determined by the other two axes. Attach the third axis to the tether, and the rotation about the second axis generates the out-of-plane motion. Without loss of generality, it is quite reasonable to assume that the individual satellite is axis-symmetric thoroughly. The participating satellites arranging in a line neatly gives rise to $I_1=I_2$, and in addition the array is axis-symmetric about the third axis~\cite{chung2008propellant1}. Hence, Eq.~(\ref{eq:3body}) reduces to

@@

which brings out that the three-satellite inline tethered system torsional rotation dynamics is irrelevant to the other two axes~\cite{chung2008propellant1}. Since the dynamic state $\omega_3$ is independent from the two axes, a simple linear feedback control can be applied to control the dynamics of the third axis, such that both $\omega_3=0$ and $\dot\omega_3 = 0$. Hence Eq.~(\ref{eq:3model}) reduces to

@@

\end{align} \begin{color}{red}From equations above, $\omega_2$ is independent from $\omega_1$. Similar to the dynamic state $\omega_3$, dynamic state $\omega_2$ can be controlled separately without affecting the in-plane dynamics~\cite{chung2007nonlinear,chung2007nonlinear1,chung2007nonlinear3}. For each satellite, three flywheels are mounted orthogonally to regulate the attitude. The flywheel which is mounted perpendicularly to the tether, governs the dynamic state $\omega_3$, and different from the other axes, the varying $\omega_3$ will not lead to the situation described in Figure~\ref{Figure:model3body}, hence a simple linear feedback control can achieve its attitude regulation. When we attention on the in-plane dynamics, the other two flywheel torques and thruster firing handle the out-plane dynamics, which can guarantee that the in-plane motion occurs without other disturbance from the other axes.\end{color} On the premise of the assumption that the out-of-plane plant is stable independently, the in-plane attitude dynamics, accordingly, can be described as a model consisting of three flywheels assembly and two tethers, as seen in Figure~\ref{Figure:model3body}. \begin{color}{red}The mathematical model expressed by using Euler-Lagrange equations is established, and the origin of the array is the satellite's geometrical center as well the mass center.\end{color} In the 2D plane, the three-body satellite array arranges along $X$-axis direction, and the positive directions of $\theta_i$ and $\phi_i$ are anticlockwise. $F_i$ denotes the $i$th thruster's linear force, and $u_i$ is defined to be the $i$th flywheel torque acting on the center of mass. $\Psi$ identifies the rotation angle, then the dynamic equation follows~\cite{chung2007nonlinear1}

@@

Hence $\vert M_1\vert = I_gml^2+m^2r^2l^2(1-\cos^2{\phi})>0$, and $M_1$ is invertible~\cite{horn2012matrix}. In the view of Lagrangian mechanics, one can get the similar result, since $M_{1}$ is a positive definite matrix~\cite{ortega2013passivity}.\end{color}

@@

Figure~\ref{Figure:modelsinglebody} shows an individual participating satellite which rotates about the center of the array frame. \begin{color}{red}Body coordinate system $x$-$y$ requires that y axis points to the direction of the increase of the array rotation angle, and meanwhile $x$-axis is along the tether\end{color}. Assume that the tether is massless and inextensible so that the vibration dynamics can be regardless. The Kevlar physical property makes the tether strong and thin enough, i.e., SPECS owns the tether consisting of four tethers lines, and the total mass is approximate to 30 \textit{kg} for 1-km-long ribbon tether\cite{chung2007nonlinear1}. \begin{color}{red}The three-satellite inline tethered frame is assumed to rotate at a specific angular rate so that the tether keeps taut.\end{color} Since the tether speed can be easily controlled by programmed tether motor and doesn't disturb any other system states, it's assumed that the tether length speed $\dot l$ is naught. Finally, assume the three-satellite inline tethered frame is manoeuvred to orbit in the second Lagrangian point of the earth-sun system referring to the SPECS project, and hence the gravity term is approximate to zero~\cite{lorenzini2006far}.\par

@@

To our knowledge, flywheels are applied as the proper actuators frequently in the attitude regulation of the satellite, for instance, the system of the SPECS project is manoeuvred by using the flywheel control strategy in most of the time~\cite{chung2008propellant1}. In the view of the mechanical structure, there are two categories of flywheels, namely, the bias moment and the zero moment. Functionally, the rotation rate of the bias moment wheels is nonnegative; the zeros moment ones can change the rotation direction. The zero moment wheels are typically known as reaction wheels, which may always maintain the whole satellite's moment zero, and are used more widely than the bias ones in the attitude regulation of the satellite. Considering the energy consumption of the system in practice, \begin{color}{red}flywheels are driven by the electricity which may be provided by energy harvesting system\end{color}, and in contrast with the thruster, the utilization of flywheels avoids consuming the limited quantities of fuel during the attitude regulation. In the aspect of regulating accuracy, the TSS need reaction wheels to generate the continuous high precise torque for the regulation in orbit, whereas thrusters consume expensive fuel to supply the linear torque output in pulse method. In addition, the reaction wheel is also convenient to equip, \begin{color}{red}and there always exists an incline reaction wheel equipped as the redundancy actuator.\end{color} For the attitude regulation, with neglecting the thruster force input, the reaction wheel control strategy changes the three-satellite inline frame into an underactuated system. More notably, the effect of the input for the control system is saturated, since the torque of an reaction wheel is not infinite. Normally, for a reaction wheel, the positive and negative torques are identical, which can be expressed by the saturation function.

@@

where $T_p$ and $T_n$ denote the maximal positive and negative torque, respectively. According to aforementioned analysis, the equations for the dynamics of the individual satellite shown in Figure~\ref{Figure:modelsinglebody} becomes

@@

Synchronization and Partial Contraction~\cite{wang2005partial}. \begin{color}{red}Consider two nominal coupled systems which have the relation\end{color}

@@

where the function $f(x,t)$ has contracting property in an input-independent matrix, then the state $x_1$ and $x_2$ will approach each other in spite of the different initial requirement.\label{theorem:syn}

@@

According to Lemma~\ref{theorem:syn}, Eq.~(\ref{eq:3bodyreduce}) indicates that the formulation of two sub-systems meets the contracting requirement, hence $(\theta_1,\phi_1)^T$ and $(\theta_1,\phi_2)^T$ will coverage to each other if an individual control law is designed to guarantee the stability of the each one~\cite{huang2015nonlinear}.\par
\begin{color}{red}In this work, the linear force is ignored, and hence the system becomes underactuated and input saturated.\end{color}

@@

In addition, $d_1(X,t)$ and $d_2(X,t)$ denote the external perturbations such as the solar pressure torque, the aerodynamic torque or the magnetic torque, and among the previous perturbations, the aerodynamic torque plays a major role, which will affect the stability of the attitude.\par
\begin{color}{red}At this point, the attitude regulation of the individual satellite expressed in Eq.~(\ref{eq:model}) has been described as an issue about the stabilization of an underactuated and coupling input system with input saturation.\end{color} Once the states of Eq.~(\ref{eq:model}) is stable, according to Lemma~\ref{theorem:syn}, the entire three-satellite array can be adjusted to be a fixed-point rotation system.

@@

\begin{color}{red}The case about attitude regulation of the three-satellite inline tethered system is converted into designing the independent control system for the individual satellite described as Eq.~(\ref{eq:model}), and meanwhile, the system is strictly saturated, coupled and nonlinear.\end{color} There exists a stable \begin{color}{red}hierarchical sliding mode (HSM)\end{color} approach investigated for a class of second order underactuated systems, like Acrobot, overhead crane and pendubot etc~\cite{wang2004design}, and the state space equations of the these models are similar to the form of Eq.~(\ref{eq:model}). Considering the effect of the input saturation, synthesize the HSM and adaptive sliding mode control schemes to obtain a modified method, which can overcome both the input saturation and coupling characteristics.\par

@@

s_2 = c_2x_3+x_4,

@@

\begin{color}{red}where $c_1$ and $c_2$ are suitable positive parameters,\end{color} and the second-level sliding surface is designed as

@@

S=\alpha s_1+\beta s_2\label{eq:S},

@@

The proceeding of the HSM design is omitted~\cite{wang2004design}. There is an important lemma for the modified controller.

@@

Considering a sort of underactuated systems which own a stabel equilibrium point, propose the sliding surfaces as Eq.~(\ref{eq:s1s2}) and Eq.~(\ref{eq:S}), and there is a approach to guaranteeing the asymptotically convergence of the second-level sliding mode. If $s_1\in L_\infty$, $\dot s_1\in L_\infty$, the first-level sliding mode also asymptotically converges.\label{lm:1}

@@

Consider the nominal nonlinear system Eq.~(\ref{eq:model}), and rewrite $\bar{sat}(u)$ as $\bar{sat}(u) = R(u)u$. Note that $0 < R(u) \le 1$

@@

where $u_{max}$ $(u_{min})$ is the maximum torque that the reaction flywheel can generate in positive (negative) direction, and there is a restriction $u_{min}<0<u_{max}$, $u_{min}=-u_{max}$ for guaranteeing the predefined condition $0<R(u)\le 1$.\par

@@

$d_1(X,t)$ and $d_2(X,t)$ are the uncertain parts of system~(\ref{eq:model}), and satisfies the following relation $max(\vert d_1(X,t)\vert,\vert d_2(X,t)\vert) \le \zeta <\infty$, \begin{color}{red}where $\zeta$ is constant positive.\end{color}\label{as:2}

@@

Modified hierarchical sliding mode control (MHSM) constructs the first- and second-level surfaces like Eq.~(\ref{eq:s1s2}) and Eq.~(\ref{eq:S}), and thanks to the Lemma~\ref{lm:1} and Assumption~\ref{as:2}, we propose the adaptive control input as follows:

@@

For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $0<\alpha\le\beta$ with $\vert x_3\vert<\pi/2$.

@@

    This can guarantee the non-singularity of Eq.~(\ref{eq:u}), when $x_3$ is varying in a small region with $\vert x_3\vert<\pi/2$. For avoiding the singularity absolutely, one can select $\alpha = \beta >0$ to remove the effect of $x_3$.

@@

The three-satellite inline array can be simplified as three individual satellite systems by above-mentioned model reduction technology, and in this section, a two-satellite array system shown in Figure~\ref{Figure:model2body} is investigated. The two satellites are the participants connected with a stiff space tether, and the dynamic equations can be described as follows:

@@

where $X = (x_1,x_2,x_3,x_4,x_5,x_6)^T$. \begin{color}{red}In addition, $\bar{sat}()$, $f_i(X,t)$ and $d_i(X,t)$ have the similar mathematical featureS which are illustrated in the individual system of three-satellite inline array in Eq.~(\ref{eq:model}),\end{color} and $f_i(X,t)$ and $b_i(X,t)$ can be derived:

@@

Hence $M_{3}$ is invertible.\end{color}\par
For applying the MHSM control to the attitude regulation of the two-satellite inline system shown in Eq.~(\ref{eq:2model}), the first-level iedal sliding surfaces are selected firstly as follows:

@@

    when $\vert\phi_1\vert<\pi/2$ and $\vert\phi_2\vert<\pi/2$.
